% !TEX root = ../LecCompile.tex

\section{Course Overview}

    %\lstinputlisting[language=python]{./code/lec01/lec01.py}

    \begin{enumerate}
        \item Lecture: Monday 12:00 - 13:00 (MP134, MP118 Overflow room)
        \item Lab: Wednesday 9:00-12:00 (MP257)
    \end{enumerate}

    Course website is just the quercus.

    Office Hours on Thursday (15:00-16:00 MP801A + Appointment)

    \href{https://github.com/mdiamon}{Professor Github}

    \textbf{Textbook:}\textit{ Computational Physics} by Mark Newman

    \subsection{Mark Scheme:}
        \begin{itemize}
            \item Lab Reports [50\%]
            \begin{itemize}
                \item Lab 1: (2024-09-30) [10\%]
                \item Lab 2: (2024-10-14) [10\%]
                \item Lab 3: (2024-10-28) [10\%]
                \item Lab 4: (2024-11-18) [10\%]
                \item Lab 5: (2024-12-02) [10\%]
            \end{itemize}
            \item Pre Lecture Quizzes [10\%]
                \begin{itemize}
                    \item Due before each lecture session
                    \item  1\% each, true false questions based on readings
                \end{itemize}
            \item Informal Lab Exercies [20\%]
                \begin{itemize}
                    \item Due at the end of each lab session. 
                    \item Submit jupyter notebook, graded for completion and effort.
                    \begin{itemize}
                        \item 0 not submitted
                        \item 1 some effort
                        \item 2 reasobable effort
                    \end{itemize}
                \end{itemize}
            \item Final Exam (in-person, during final exam period) [20\%]
                \begin{itemize}    
                    \item Open book, open notes, \textbf{no electronic devices}.
                    \item Going to be like a Comp Sci exam
                \end{itemize}
        \end{itemize}

    Remarks must be requested within \textbf{2 weeks} of grading. Must specifically state what you want regraded. Grades are only considered offical at the end of the term (when posted on ACORN).

    \subsection{Course Outline}
        \begin{itemize}
            \item Introduction to Python
            \item Python Ecosystem
            \item Numerical Integration
            \item Derivatives and Interpolation
            \item Solving linear and non-linear equations
            \item Fourier Transforms
            \item Solving simple ODEs
            \item Solving simple PDEs
            \item Random processes \& Monte Carlo Methods
            \item Prof Demos, Advanced Fitting, \& Optimization
            \item (Optional) Intro Machine Learning
        \end{itemize}

\section{General Problem Solving Approach}
    \begin{enumerate}
        \item \textbf{Mathematical Model}
        \item \textbf{Translate \& Discretize (Operationalize)}: Setup discrete arrays of independent variables, dependent variavles and defin operators on these variables accordin to the model.
        \item \textbf{Initialize}
        \item \textbf{Evaluate}
        \item \textbf{Debug}
        \item \textbf{Analyze}: Processing (figures, etc.)
        \item \textbf{`'Sanity Check''}: Check if output makes sense with intuition.
    \end{enumerate}

\section{Review fo Next session}
